Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-06-16 arxiv/template.tex
typos

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{Proper radial distance}

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={Proper radial distance as a coordinate in the Schwarzschild metric}
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Robin K. S.~Hankin}
pdfkeywords={Black holes, Schwarzschild metric, proper distance,
}

\begin{document}
\maketitle

>>>>

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
%\renewcommand{\shorttitle}{Proper radial distance}

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={Proper radial distance as a coordinate in the Schwarzschild metric},
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Robin K. S.~Hankin},
pdfkeywords={Black holes, Schwarzschild metric, proper distance}
}
\begin{document}
\maketitle
